Kindly Bent to Free Us

### 2019-07-11 kindly/lang.tex
checkpoint
Fix ref.

The rest of this section formalizes  \lang: the syntax (\cref{syntax}),
the statics in terms of syntax directed typing (\cref{sdtyping}),
and a dynamics that is linearity- and resource-aware (\cref{sem}).

@@

% \clearpage
\subsection{Semantics}
\label{sem}
\input{internal-grammar}

>>>>

The rest of this section formalizes  \lang: the syntax (\cref{syntax}),
the statics in terms of syntax directed typing (\cref{sdtyping}),
and a dynamics that is linearity- and resource-aware (\cref{sec:sem}).

@@

% \clearpage
\subsection{Semantics}
\label{sec:sem}
\input{internal-grammar}
